\chapter*{Abstract}                      % ne pas numéroter
\phantomsection\addcontentsline{toc}{chapter}{Abstract} % inclure dans TdM
\thispagestyle{fancy}
\vspace{-2cm}
The term UX (User Experience) refers to the quality of the user's experience in any interaction situation. The primary objective of our internship was to develop a computer solution to increase the quality of service of the IZIWAY CAMEROON application. This solution addresses problems such as the low user rate, the low conversion rate (number of purchases) on the platform, the lack of animation on the application. With regard to these various problems, we worked on how to optimize the mobile application of a company that is in E-commerce. In this perspective, we opted for the agile method, more precisely the SCRUM methodology because of the complexity of the project and especially because this work methodology puts the customer at the center of the activities.  The IZIWAY CAMEROUN application is based on the MVC architecture, all the interfaces have been developed with the Flutter Framework, the interactions with the database stored in the database management system MYSQL SERVER are done through an api which has been developed in Csharp. In view of the above, we can say that there is a clear improvement on the ergonomics of the application which contributes to the increase of the number of users and increases the conversion rate (purchase rate) on our platform. The solution offered as a result of our work is a success because of the satisfaction of the top management of IZIWAY CAMEROON and that of the employees who did not fail to signify a clear improvement in their work.\\


\textit{Keywords} : Marketplace, User experience, Purchasing process.